% Bensako 2.3, 2.7, 2.8, 2.9, 2.29
% Williams PS
% Case 11
% Pindyck 3
% Mankiw 2, 10


\documentclass{article}
\title{Supply \& Demand Classwork}
\author{Principles of Microeconomics}
\date{\today}

\begin{document}

\maketitle

\subsection*{Instructions} Please answer on a separate sheet of paper and submit on Gradescope by the end of class. You must turn in the required problems. You may turn in the bonus problems for extra credit on tomorrow's quiz.

\subsection*{Required}

\begin{enumerate}

\item "An increase in demand for notebooks raises the quantity of notebooks demanded but not the quantity supplied." Is this statement true or false. Please explain in a sentence.

\item The market for pizza has the following demand and supply schedules:

	\begin{center}
	\begin{tabular}{c c c}
	\textbf{Price} & \textbf{Quantity Demanded} & \textbf{Quantity Supplied} \\
	\hline
	\$4 & 135 pizzas & 26 pizzas \\
	5 & 104 & 53 \\
	6 & 81 & 81 \\
	7 & 68 & 98 \\
	8 & 53 & 110 \\
	9 & 39 & 121
	\end{tabular}
	\end{center}

	\begin{enumerate}
	
	\item What is the equilibrium price and quantity in this market? No explanation necessary. 
	
	\item If the actual price in this market were \textit{above} the equilibrium price, what would drive the market toward the equilibrium? Please explain in a sentence.
	
	\item If the actual price in this market were \textit{below} the equilibrium price, what would drive the market toward the equilibrium? Please explain in a sentence.
	
	\end{enumerate}

\item Consider the following events: Scientists reveal that eating oranges decreases the risk of diabetes, and at the same time, farmers use a new fertilizer that makes orange trees produce more oranges. Please illustrate what effect these changes have on the equilibrium price and quantity of oranges, and summarize your diagram in a sentence.

\item Because bagels and cream cheese are often eaten together, they are complements.

	\begin{enumerate}
	
	\item We observe that both the equilibrium price of cream cheese and the equilibrium quantity of bagels have risen. What could be responsible for this pattern -- a fall in the price of flour or a fall in the price of milk? Please draw a supply-and-demand diagram and summarize it in a sentence.
	
	\item Suppose instead that the equilibrium price of cream cheese has risen but the equilibrium quantity of bagels has fallen. What could be responsible for this pattern -- a rise in the price of flour or a rise in the price of milk? Please illustrate your answer and summarize your diagram in a sentence. 
	
	\end{enumerate}
	
\item Suppose that the price of baseball tickets at your future college is determined by market forces. Currently the demand and supply schedules are as follows:

	\begin{center}
	\begin{tabular}{c c c}
	\textbf{Price} & \textbf{Quantity Demanded} & \textbf{Quantity Supplied} \\
	\hline
	\$4 & 10,000 tickets & 8,000 tickets \\
	8 & 8,000 & 8,000 \\
	12 & 6,000 & 8,000 \\
	16 & 4,000 & 8,000 \\
	20 & 2,000 & 8,000
	\end{tabular}
	\end{center}
	
	\begin{enumerate}
	
	\item What is unusual about this supply curve? Why might this be the case?
	
	\item What are the equilibrium price and quantity of tickets? No explanation necessary. 
	
	\item Your future college plans to increase total enrollment next year by 5,000 students. The additional students will have the following demand schedule:
	
	\begin{center}
	\begin{tabular}{c c}
	\textbf{Price} & \textbf{Quantity Demanded} \\
	\hline
	\$4 & 4,000 tickets \\
	8 & 3,000 \\
	12 & 2,000 \\
	16 & 1,000 \\
	20 & 0 \\
	\end{tabular}
	\end{center}
	
	What will be the new equilibrium price and quantity next year? Please show the relevant calculations. 
	
	\end{enumerate}
	
\end{enumerate}

\subsection*{Bonus}

\begin{enumerate}
\setcounter{enumi}{5}
	
\item Ketchup is a complement (as well as a condiment) for hot dogs. If the price of hot dogs rises, what happens to the market for ketchup? For tomatoes? For tomato juice? For orange juice. Please explain in up to four sentences and four supply-and-demand diagrams.

\item Suppose that global demand for kombucha is $Q_D = 144 - 12P$, and global supply is $Q_S = 16 + 4P$.

	\begin{enumerate}
	
	\item What is the equilbrium in the global kombucha market?
	
	\item Suppose domestic (i.e. not foreign) demand for kombucha is $Q_D = 80 - 8P$, and suppose foreign demand increases by 50\%. What is the new equilibrium price in the global kombucha market?
	
	\end{enumerate}

\end{enumerate}

\end{document}