\documentclass{article}

\title{Supply \& Demand Together Problem Set}
\author{Principles of Microeconomics}
\date{\today}

\begin{document}

\maketitle

\subsection*{Instructions} Please answer on a separate sheet of paper and submit on Gradescope. 

\subsection*{Multiple Choice} Please briefly explain your choice with a sentence or a diagram.

\begin{enumerate}

\item The discovery of a large new reserve of crude oil will shift the \underline{\phantom{xxxxxxxxxx}} curve for gasoline, leading to a \underline{\phantom{xxxxxxxxxx}} equilibrium price.

	\begin{enumerate}
	
	\item supply; higher
	
	\item supply; lower
	
	\item demand; higher
	
	\item demand; lower
	
	\end{enumerate}
	
\item If the economy goes into a recession and incomes fall, what happens in the markets for inferior goods?

	\begin{enumerate}
	
	\item Prices and quantities both rise.
	
	\item Prices and quantities both fall.
	
	\item Prices rise and quantities fall.
	
	\item Prices fall and quantities rise.
	
	\end{enumerate}
	
\item Which of the following might lead to an increase in the equilibrium price of jelly and a decrease in the equilibrium quantity of jelly sold?

	\begin{enumerate}
	
	\item an increase in the price of peanut butter, a complement to jelly
	
	\item an increase in the price of Marshmallow Fluff, a substitute for jelly
	
	\item an increase in the price of grapes, an input into jelly
	
	\item an increase in consumers' incomes as long as jelly is a normal good
	
	\end{enumerate}

\end{enumerate}

\subsection*{Free Response}

\begin{enumerate}
\setcounter{enumi}{3}

\item Soda and pizza are complements because they are often enjoyed together. When the price of soda rises, what happens to the supply, demand, quantity supplied, quantity demanded, and price in the market for pizza? Please draw a supply-and-demand diagram and summarize it in a sentence.

\item Please explain each of the following statements using supply-and-demand diagrams and a summarizing sentence.

	\begin{enumerate}
	
	\item "When a cold snap hits Florida, the price of orange juice rises in supermarkets throughout the country.,"
	
	\item "When the weather turns warm in New England every summer, the price of hotel rooms in Caribbean resorts plummets."
	
	\item "When a war breaks out in the Middle East, the price of gasoline rises, and the price of a used Cadillac falls."
	
	\end{enumerate}
	
\item Consider the market for minivans. For each of the events listed here, please draw a diagram to show the effect on the price and quantity of minivans.

	\begin{enumerate}
	
	\item People decide to have more children.
	
	\item A strike by steelworkers raises steel prices.
	
	\item Engineers develop new automated machinery for the production of minivans.
	
	\item The price of sports utility vehicles rises.
	
	\item A stock market crash lowers people's income.
	
	\end{enumerate}
	
\item Consider the markets for film streaming services, TV screens, and tickets at movie theaters.

	\begin{enumerate}
	
	\item Suppose a technological advance reduces the cost of manufacturing TV screens. Please draw a diagram to show what happens in the market for TV screens, and summarize your diagram in a sentence.
	
	\item Please draw two more diagrams to show how the change in the market for TV screens affects the markets for film streaming and movie tickets. Summarize your diagrams with one sentence each. 
	
	\end{enumerate}
	
\item How long did this problem set take you?

\end{enumerate}

\end{document}

% Problems #1, 2, 3, 4, 5, 6

