\documentclass{article}

\title{Supply Problem Set}
\author{Principles of Microeconomics}
\date{\today}

\begin{document}

\maketitle

\subsection*{Instructions} Please answer on a separate sheet of paper and submit on Gradescope. 

\subsection*{Multiple Choice} Please briefly explain your choice. One sentence is sufficient.

\begin{enumerate}

\item Which of the following moves the pizza market up along a given supply curve?

	\begin{enumerate}
	
	\item an increase in the price of pizza
	
	\item an increase in the price of root beer, a complement to pizza
	
	\item a decrease in the price of cheese, and input to pizza
	
	\item a kitchen fire that destroys a popular pizza joint
	
	\end{enumerate} 
	
\item Which of the following shifts the supply curve for pizza to the right?

	\begin{enumerate}
	
	\item an increase in the price of pizza
	
	\item an increase in the price of root beer, a complement to pizza
	
	\item a decrease in the price of cheese, and input to pizza
	
	\item a kitchen fire that destroys a popular pizza joint
	
	\end{enumerate}
	
\item Movie tickets and film streaming services are substitutes. If the price of film streaming increases, what happens in the market for movie tickets?

	\begin{enumerate}
	
	\item The supply curve shifts to the left.
	
	\item The supply curve shifts to the right.
	
	\item The demand curve shifts to the left.
	
	\item The demand curve shifts to the right.
	
	\end{enumerate}

\end{enumerate}

\subsection*{Free Response}

\begin{enumerate}
\setcounter{enumi}{3}

\item Does a change in producers' technology lead to a movement along the supply curve or to a shift in the supply curve? Does a change in price lead to a movement along the supply curve or to a shift in the supply curve. No explanation necessary.

\item When a cold snap hits Florida, what happens to the supply curve for orange juice? One sentence is sufficient.

\item Consider the market for minivans. For each of the events listed here, explain whether supply increases or decreases. One sentence for each is sufficient.

	\begin{enumerate}
	
	\item A strike by steelworkers raises steel prices.
	
	\item Engineers develop new automated machinery for the production of minivans.
	
	\end{enumerate}
	
\item What effect does each of the following have on supply for sweatshirts? One sentence for each is sufficient. 

	\begin{enumerate}
	
	\item A hurricane in South Carolina damages the cotton crop.
	
	\item New knitting machines are invented. 
	
	\end{enumerate}
	
\item How long did this problem set take you?

\end{enumerate}

\end{document}

%Supply ---
% QQ #7-9
% QfR #6
% P&A #1ac, 3bc, 4b, 6ad